### 2024-11-11 conteudo/eval/eval.tex
add initial text of preliminar

>>>>

To finalize this report, we present the current state of our research. As of the 
time of writing, we have finished \textbf{Phase I} of this research, 
which includes the implementation of 
the proposed tool and the evaluation of the tool through both formal literature 
and empirical analyses. This chapter begins with the presentation of the results 
from the tool evaluation. Next, we present a preliminary experiment we are currently 
conducting to assess the viability of our Ethnographic Study. Finally, we outline 
the next steps in this research.
